---
title: "Writing Code"
author: "Renato Erazo"
date: "2 de octubre de 2020"
output:
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Directorio de trabajo

Consultar el directorio de trabajo
```{r}
getwd()
```
Ver el contenido de un directorio
```{r}
dir()
```
Que se encuentra en el workspace
```{r}
ls()
```

##  Leer url

```{r}
con <- url("http://www.jhsph.edu","r")
x <- readLines(con)
head(x)
```
## Indexando listas, puede extra
```{r}
x <- list(foo = 1:4, bar = 0.6, baz = "hello")
x[c(1,3)] #Extrae la columna 1 y 3
```
## Removind NA Values
```{r}
x <- c(1,2,NA,4,NA,5)
bad <- is.na(x)
bad
x[!bad]
```
```{r}
x <- c(1,2,NA,4,NA,5)
y <- c("a","b",NA,"d",NA,"f")
good <- complete.cases(x,y)
good
x[good]
y[good]

y <- c(NA,"b",NA,"d",NA,"f")
good <- complete.cases(x,y)
good
x[good]
y[good]
```

```{r}
airquality
good <- complete.cases(airquality)
airquality[good,]
```
## ----- Examen What is the meaning of Ozone in this dataset?
```{r}
hw1_data <- read_csv("hw1_data.csv")
w <- complete.cases(hw1_data$Ozone)
mean(hw1_data[w,]$Ozone)
```
# What was the maximum ozone value in the month of May
```{r}
may <- hw1_data$Month == 5
ozone_valid <- complete.cases(hw1_data$Ozone)
condiciones <- may & ozone_valid
max(hw1_data[condiciones,]$Ozone)
```
#What is the mean of "Temp" when "Month" is equal to 6
```{r}
month6 <- hw1_data$Month == 6
mean(hw1_data[month6,]$Temp)
```
#Wxtrac the subset of rows of the data frame where Ozone ara above 31 and Temp valie are above 90, what is the mean of Solar.R in this subset
```{r}

```

