---
title: "Assigment3Ver2"
author: "Renato Erazo"
date: "1/11/2020"
output:
  pdf_document: default
  html_document: default
---

## Introduction
Download the le ProgAssignment3-data.zip le containing the data for Programming Assignment 3 from
the Coursera web site. Unzip the le in a directory that will serve as your working directory. When you
start up R make sure to change your working directory to the directory where you unzipped the data.
The data for this assignment come from the Hospital Compare web site (http://hospitalcompare.hhs.gov)
run by the U.S. Department of Health and Human Services. The purpose of the web site is to provide data and
information about the quality of care at over 4,000 Medicare-certied hospitals in the U.S. This dataset es-
sentially covers all major U.S. hospitals. This dataset is used for a variety of purposes, including determining
whether hospitals should be ned for not providing high quality care to patients (see http://goo.gl/jAXFX
for some background on this particular topic).
The Hospital Compare web site contains a lot of data and we will only look at a small subset for this
assignment. The zip le for this assignment contains three les
• outcome-of-care-measures.csv: Contains information about 30-day mortality and readmission rates
for heart attacks, heart failure, and pneumonia for over 4,000 hospitals.
• hospital-data.csv: Contains information about each hospital.
• Hospital_Revised_Flatfiles.pdf: Descriptions of the variables in each le (i.e the code book).
A description of the variables in each of the les is in the included PDF le named Hospital_Revised_Flatfiles.pdf.
This document contains information about many other les that are not included with this programming
assignment. You will want to focus on the variables for Number 19 (\Outcome of Care Measures.csv") and
Number 11 (\Hospital Data.csv"). You may nd it useful to print out this document (at least the pages for
Tables 19 and 11) to have next to you while you work on this assignment. In particular, the numbers of
the variables for each table indicate column indices in each table (i.e. \Hospital Name" is column 2 in the
outcome-of-care-measures.csv le).

# Read data

### Read the outcome data into R via the read.csv function and look at the frst few rows.



```{r}
outcome <- read.csv("outcome-of-care-measures.csv", colClasses = "character")
head(outcome)
```
```{r}
outcome <- read.csv("outcome-of-care-measures.csv")
```

There are many columns in this dataset. You can see how many by typing ncol(outcome) (you can see the number of rows with the nrow function). In addition, you can see the names of each column by typing names(outcome) (the names are also in the PDF document.
To make a simple histogram of the 30-day death rates from heart attack (column 11 in the outcome dataset), run.

Because we originally read the data in as character (by specifying colClasses = "character" we need to coerce the column to be numeric. You may get a warning about NAs being introduced but that is okay.

```{r}
outcome[,11] <- as.numeric(outcome[,11])

hist(outcome[,11])
```

## 2 Finding the best hospital in a state

Write a function called best that take two arguments: the 2-character abbreviated name of a state and an outcome name. The function reads the outcome-of-care-measures.csv file and returns a character vector with the name of the hospital that has the best (i.e. lowest) 30-day mortality for the specified outcome in that state. The hospital name is the name provided in the Hospital.Name variable. The outcomes can be one of \heart attack", \heart failure", or \pneumonia". Hospitals that do not have data on a particular outcome should be excluded from the set of hospitals when deciding the rankings.

Handling ties. If there is a tie for the best hospital for a given outcome, then the hospital names should be sorted in alphabetical order and the frst hospital in that set should be chosen (i.e. if hospitals \b", \c", and \f" are tied for best, then hospital \b" should be returned). 

#Funcions para validar datos de entrada

```{r}

validar <-function(ds,s,r)
{
  ## To Propercase
 # if ("package:stringi" %in% search())
  #{
   # install.packages("stringi")
  #}
  library(stringi)
  require(stringi)
  
  r <- stri_trans_general(r, id = "Title")
  
  print(r)
  
  
  ## Read outcome data
  outcome <- read.csv(ds, colClasses = "character")
  
  ## Check that state and outcome are valid
  
  estadoOk <- sum(sapply(outcome$State,function(x) x == s)) == 0
  
  if (estadoOk) {
     
      stop('Invalid state')
    }
  
  
  tipoRest <- c("Heart Attack", "Heart Failure", "Pneumonia")
  siTipo <- sum(sapply(tipoRest,function(x) x == r)) == 0
  
  if(siTipo){
   
        stop('Invalid outcome')
  }
  outcome
}
```




The function should use the following template.

```{r}
best <- function (state, restriccion)
{
  
  restriccion <- stri_trans_general(restriccion, id = "Title")
  outcome <- validar(ds = "outcome-of-care-measures.csv",s = state,r = restriccion)
  
  
  
  ## Return hospital name in the sate with lowest 30-day death
  
  library(dplyr)
  prefijo <- "Lower.Mortality.Estimate...Hospital.30.Day.Death..Mortality..Rates.from"
  indice <- sub(" ",".",restriccion)
  completo <- paste(prefijo,indice,sep = ".")
  subOutcome <- outcome %>% select(State,Hospital.Name,completo)
  
  ## ---- Cambio los nombre de columnas mas simple
  
  names(subOutcome) = c("Estado","Hospital","Data")
  
  ## --- Solo recuperar datos del estado/provincia seleccionado
  subOutcome <- subset(subOutcome,Estado == state)
  
  
 
  
  #texto a número

  subOutcome$Data  <- as.numeric(subOutcome$Data)
  
   ## --- Eliminar NA
  
  subOutcome <- subOutcome %>% filter(!is.na(Data))
  
  
  

  ## rate
  
  
  
  
  
  subOutcome <- subOutcome %>% arrange(Data)
  
  #---- Iterar entre los valores menores
  
  mejor <- subOutcome[1,3]
  
  # --- Extraere los mejores
  
subOutcome %>% filter(Data == mejor) %>% arrange(Data)
  
  
  
}






```
## -----------------  Ejemplos
```{r}
best("LA","heart Attack")
```

## ---- 3Ranking hospitals by outcome in a state

Write a function called rankhospital that takes three arguments: the 2-character abbreviated name of a
state (state), an outcome (outcome), and the ranking of a hospital in that state for that outcome (num).
The function reads the outcome-of-care-measures.csv le and returns a character vector with the name
of the hospital that has the ranking specied by the num argument. For example, the call
rankhospital("MD", "heart failure", 5)
would return a character vector containing the name of the hospital with the 5th lowest 30-day death rate
for heart failure. The num argument can take values \best", \worst", or an integer indicating the ranking
(smaller numbers are better). If the number given by num is larger than the number of hospitals in that
state, then the function should return NA. Hospitals that do not have data on a particular outcome should
be excluded from the set of hospitals when deciding the rankings.
Handling ties. It may occur that multiple hospitals have the same 30-day mortality rate for a given cause
of death. In those cases ties should be broken by using the hospital name. For example, in Texas (\TX"),
the hospitals with lowest 30-day mortality rate for heart failure are shown here.

```{r}
rankhospital <- function(state, restriccion, num = "best") {
  ## Read outcome data
  ## Check that state and restriccion are valid
  
  require(stringi)
  
  restriccion <- stri_trans_general(restriccion, id = "Title")
 
  
  
  ## Read outcome data
  outcome <- read.csv("outcome-of-care-measures.csv", colClasses = "character")
  
  ## Check that state and outcome are valid
  
  estadoOk <- sum(sapply(outcome$State,function(x) x == state)) == 0
  
  if (estadoOk) {
    
    stop('Invalid state')
  }
  
  tipoRest <- c("Heart Attack", "Heart Failure", "Pneumonia")
  siTipo <- sum(sapply(tipoRest,function(x) x == restriccion)) == 0
  if(siTipo){
    
    stop('Invalid outcome')
  }
  ## 2.-Validar que sean "best", "worst" número y menor al número de provincias
  
  ## 2.1.-  --- Primero se valida si es un número y si este es menora a los casos del estado
  
  ## 2.1.1.- contruimos el nombre de la columna para rate
  
  library(dplyr)
  prefijo <- "Hospital.30.Day.Death..Mortality..Rates.from"
  indice <- sub(" ",".",restriccion)
  completo <- paste(prefijo,indice,sep = ".")
  outcome <- outcome %>% select(State,Hospital.Name,ZIP.Code,completo)
  
  
  ## ---- Cambio los nombre de columnas mas simple
  
  names(outcome) = c("Estado","Hospital","ZIP","Rate")
  
  ## --- Solo recuperar datos del estado/provincia seleccionado
  outcome <- subset(outcome,Estado == state)
  
 
  if( num != "best" && num != "worst" && num%%1 != 0 ) {
    stop("invalid num")
  }
  
  #texto a número
  
  outcome$Rate  <- as.numeric(outcome$Rate)
  
  ## --- Eliminar NA
  
  outcome <- outcome %>% filter(!is.na(Rate))
  
  ##En este momento se puede validar el número de filas
  if(num == "best")
    num <- 1
  if(num == "worst")
    num <- nrow(outcome)
  if(num > nrow(outcome))
    stop('NA')
  
  #Ordenar por Rate y nombre de hospital
  
  outcome <- outcome %>% arrange(Rate,Hospital)
  
  
  ## Return hospital name in that state with the given rank
  
  outcome[num,]$Hospital
  
  ## 30-day death rate
  
  
  
}
```

#---- Ejemplo

```{r}
rankhospital("TX", "heart failure", 4)

```
```{r}
rankhospital("MD", "heart attack", "worst")
```
```{r}

rankhospital("MN", "heart attack", 5000)
```

